---
title: "Lecture_2"
output: html_document
---

## Notes about assigned Readings
```{r, eval=FALSE}
- [ ] Huntington-Klein, N. – Chapter 2
https://theeffectbook.net/ch-ResearchQuestions.html
Table of Contents
- [x] ﻿﻿﻿2.1 What Is a Research Question?
* a research question is a question that can be answered, and for which having that answer will improve your understanding of how the world works.
- [x] ﻿﻿﻿2.2 Why Start with a Question?
* Without a disciplined research question, there’s no reason not to just check everything! Something is going to pop up as related by random chance if you check enough stuff. 
- [x] ﻿﻿﻿2.3 Where Do Research Questions Come From?
* Research questions can come from lots of places. Mostly, curiosity. We want to know how the world works, and that naturally leads to questions!
* There are two steps in this process: thinking about theory, and coming up with a research question. Either one can come first.
- [x] ﻿2.4 How Do You Know if You've Got a Good One?
* First, consider the potential answers you might get. Then, imagine what kind of sense you’d make of that result, or what conclusion you would draw.

```

## Notes from lecture
- You can find a statistical realtionship in pretty much anything. 
- 3 Types of  research questions
- Descriptive
- Predictive
- Causal
- HW: Choose and think about the research question for 
- Working with a sample is easier.
- Question: What is the name of the dataset we are working with for this quarter and how do I download it? 
- Question: Lecture Slide 9, How many variable types are there? Three?
- [Insert photo of the slide here]
- Question: Lecture Slide 11, ...
- [Insert photo of the slide here]
- When loading the libraries, notice the conflicts section. Conflicts - there is a function called filter(), if you want to use it, you must indicate which package you want it work with. Should I use it for dplyr or stats? Using from dplyr(), then you will have to indicate that.
- [HW Insert screenshot of the console here]

```{r}
getwd()
setwd("/Users/zacharyjohnigan/Library/CloudStorage/OneDrive-TheUniversityofChicago/UChicago Student/Quarter 8 - Summer 2026/2 Data For Policy Analys:Mgmt/Week 1/DFPAM_Lecture_2/DFPAM_Lecture_2")
```

```{r}
getwd()
list.files()
```

```{r}
write.csv(da37941.0005, file = "37941-0005-Data.csv", row.names = FALSE)
```

## Group Work
can be answered using quantitative data and is related to social policy.

##### Policy Field
Environmental Policy

##### Question Type
Causal: How do organic vs non-organic foods affect consumer's ability to meet everyday living expenses?

##### Data: 
Survey data, those who consume organic foods.

##### Example Question: 
"Was your decision to purchase or not purchase organic foods based upon your finances?"

##### Who would be included in the data set: 
Those undergraduate students at UChicago who either recieve or don't financial aid. Knowing that UChicago has a high percentage of studetents in the 1% (change this word later), and knowing that those who receive financial aid is a good determinant of being within the other 99%.




## Group Work 2

For each variable, determine:

##### Variable 1
• CB9_AGECAT_SERVE_SA - Type (Serves School-age Children)

Type of variable (measurement scale):
• Nominal

Form of the variable:
• Discrete


##### Variable 2
• CB9_AGECAT_SERVE_1

Type of variable (measurement scale):
• Interval/Ratio - Numeric values with meaningful difference (0 for no, 1 for yes)

Form of the variable:
• Discrete - 
